---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, fig.width = 10, fig.height = 6)

```

```{css}
p {
  line-height: 1.6;
  margin-bottom: 12px;
}

h2 {
  color:#ED254E;
  font-weight: bold;
  font-family: Arial, sans-serif;
}

body {
  padding: 30px;
  background-color: #fdfdfd;
}

```

## Coffee Drinking Habits of University Students
```{r}
library(tidyverse)

#Here is my csv
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQFhtTS3mmF-P5BVMnWuXrAbFk1w4Kl-jpnKAV4NMeL6GBf5NjmgGCHGnT_XH87KMKGPfoUxgAs6UOE/pub?gid=79483515&single=true&output=csv")

#Now I wanna see the data frame
glimpse(logged_data)

#rename the variables
latest_data <- logged_data %>%
  rename(
    cups_per_day = `On average, how many cups of coffee do you drink per day?`,
    coffee_type = `What type of coffee do you drink most often?`,
    coffee_source = `Where do you usually get your coffee from?`
  )
```


1.  We begin by summarising the data with two key values: - the **average number of cups of coffee** students drink per day, and - the **total number of responses** we received in our survey.

```{r}
mean(latest_data$cups_per_day, na.rm = TRUE)
nrow(latest_data)

```

*So The average number of cups of coffee students drink per day is `r round(mean(latest_data$cups_per_day, na.rm = TRUE), 1)`. A total of `r nrow(latest_data)` responses were collected.*

2.  The first bar chart shows the **most common type of coffee** students reported that they drank. This tells us about the general coffee preferences of the group.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = coffee_type),
           fill = "#a3c4de") +
  labs(title = "Most Common Coffee Type",
   x = "Type of Coffee",
    y = "Number of Responses"
   )
```

3.  The second bar graph shows **where students generally get their coffee from**, such as chain coffeehouses, college coffeehouses, or those made at home. This tells us something about students' coffee-consumption patterns.

```{r}
ggplot(data = latest_data) + 
  geom_bar(aes(x = coffee_source),
           fill = "#c3cdc4") +
  labs(title = "Where Students Get Their Coffee",
       x = "Source",
       y = "Number of Responses"
  )
```
